A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-06-22 03_Prep_data.Rmd
Work on loop
Move constant outside the loop, `Tcrit`.

Revise to use more standard notation, `i` in the loop in place of `Trial2012` to make it more readable to most users familiar with loop syntax

```{r all_LSD_trials}
Trials <- PM_MB_means %>%
   filter(Y_error_type == "lsd (P=0.05)") %>%
   select(trial_ref) %>%
   distinct()
Trials
```
Let's use this list of trials to subset the data and calculate sampling variances.

@@

```{r LSD_2_Sampling_Variance}

for (Trial2012 in Trials$trial_ref) {
   Tcrit <-
      1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups; This value is the same for both trials "mung1112/01" and "mung1112/02"
   DFw <-
      sum(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates) -
      length(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates) # degrees of freedom within groups

   LSD <-
      PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$yield_error[1]

   V_yield <-
      (PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[1] * (LSD /
                                                                            Tcrit) ^ 2) / 2 # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221

   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates)) {
      if (j == 1) {
         Sv <-
            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates))
      } # reset Sv vector if this is the first loop

      Sv[j] = V_yield /
         PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[j]

@@

   # Replace the values in the dataset
   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$yield_error <-
      Sv
   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Y_error_type <-
      "SamplingVariance"

@@

### Converting standard deviation to sample variance
Now to estimate the variance from the standard deviation

>>>>

```{r all_LSD_trials}
Trials <- PM_MB_means %>%
   filter(Y_error_type == "lsd (P=0.05)") %>%
   select(trial_ref) %>%
   distinct()
Trials
```

Let's use this list of trials to subset the data and calculate sampling variances.

@@

`Tcrit` is the T critical value for which there is significant difference between two groups.
This value is the same for both trials "mung1112/01" and "mung1112/02".

```{r LSD_2_Sampling_Variance}
Tcrit <- 1.697 # 0.05 and DFw = 30

for (i in Trials$trial_ref) {
   DFw <-
      sum(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates) -
      length(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates) # degrees of freedom within groups

   LSD <-
      PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error[1]

   V_yield <-
      (PM_MB_means[PM_MB_means$trial_ref == i,]$replicates[1] * (LSD /
                                                                            Tcrit) ^ 2) / 2 # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221

   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates)) {
      if (j == 1) {
         Sv <-
            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates))
      } # reset Sv vector if this is the first loop

      Sv[j] = V_yield /
         PM_MB_means[PM_MB_means$trial_ref == i,]$replicates[j]

@@

   # Replace the values in the dataset
   PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <-
      Sv
   PM_MB_means[PM_MB_means$trial_ref == i,]$Y_error_type <-
      "SamplingVariance"

@@

### Converting standard deviation to sample variance

Now to estimate the variance from the standard deviation.
